Adolescent well-being in the digital age

### 2022-06-30 00-clean.Rmd
wip 2022-06-30

```{r setup, include = FALSE}
#| cache: false
#| results: hide
#| message: false
# Packages
library(readxl)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(labelled)
library(countrycode)
library(lubridate)
library(gtsummary)
library(kableExtra)
library(tidyverse)

>>>>

```{r setup, include = FALSE}
#| cache: false
#| results: hide
#| message: false
# Packages
library(readxl)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(labelled)
library(countrycode)
library(lubridate)
library(kableExtra)
library(tidyverse)

### 2022-06-30 00-describe.Rmd
Don't load anything in .Rprofile
wip 2022-06-30

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(ggstance)
library(ggh4x)
library(mgcv)
library(tidyverse)

@@

@@

```{r}
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  group_by(Dataset, region, outcome, country) %>% 
  summarise(
    n_n = sum(n),
    n_year = length(unique(year))
  ) %>% 
  summarise(
    N = sum(n_n), 
    Years = mean(n_year)
  ) %>%
  summarise(
    N_sum = round(mean(N)), 
    Years_mean = round(mean(Years))
  ) %>%
  kbl(caption = "Dataset summary") %>% 
  kable_custom()
gwp %>% 
  group_by(outcome) %>% 
  summarise(n=sum(n)) %>% 
  summarise(N=comma(median(n)))
```

Number of data points per outcome

```{r}
unique(gwp$age)
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  count(Dataset, outcome)
itu %>% 
  drop_na(internet)

```

@@

```{r trends-regions}
#| echo: false
#| fig-width: 12
#| fig-height: 8
#| fig-cap: "Trends in all variables across regions"
#| label: fig-trends-regions

@@

itu <- read_rds("data/itu.rds") %>%
  select(
    region, country, year,
    Internet = internet,
    Mobile = mobile
  ) %>%
  # Truncate mobile percentages for figure
  mutate(Mobile = if_else(Mobile > 1.5, NaN, Mobile)) %>%
  pivot_longer(
    c(Internet, Mobile),
    names_to = "outcome", values_to = "val"
  )

@@

tmp_country %>%
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = ~percent(., .1),
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, outcome)),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  geom_line(
    data = tmp_region %>% mutate(year = make_date(year)),
    aes(y = .fitted, group = interaction(region, outcome)),
    alpha = 1, size = .6, color = "dodgerblue4"
  ) +
  geom_line(
    data = tmp_world %>% mutate(year = make_date(year)),
    aes(y = .fitted, group = interaction(region, outcome)),
    alpha = 1, size = .8, color = "dodgerblue4"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    aspect.ratio = 1,
    legend.position = "none",
    panel.spacing.x = unit(4, "pt"),
    panel.spacing.y = unit(6, "pt"),
    axis.title.y = element_blank()
  )
agg_png(
  "figures/Fig-trends-data.png",
  width = W, height = W*0.8, units = "in", res = 400
)
last_plot()
dev.off()
```

>>>>

```{r setup, include = FALSE}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(ggstance)
library(ggh4x)
library(gtsummary)
library(mgcv)
library(plotly)
library(tidyverse)

# Common options
source("_common.R")

@@

Here are some descriptives of the datasets.

## Sample summaries

@@

```{r}
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  group_by(Dataset, region, outcome, country) %>% 
  summarise(
    n_n = sum(n),
    n_year = length(unique(year))
  ) %>% 
  summarise(
    N = sum(n_n), 
    Years = mean(n_year)
  ) %>%
  summarise(
    N_sum = round(mean(N)), 
    Years_mean = round(mean(Years))
  ) %>%
  kbl(caption = "Number of respondents and years by outcome and region") %>% 
  kable_custom()
tmp <- gwp %>% 
  group_by(outcome) %>% 
  summarise(n=sum(n)) %>% 
  summarise(N=comma(median(n))) %>% 
  pull(N)
```

The median number of respondents per Gallup well-being outcome was `r tmp`, and the unique age bins in the GWP data were `r unique(gwp$age)`.

We then examined the total number of observations (cell means and SEs) per outcome

```{r}
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  count(Dataset, outcome) %>% 
  bind_rows(
    itu %>% 
      select(internet, mobile) %>% 
      pivot_longer(everything(), names_to = "outcome") %>% 
      drop_na(value) %>% 
      count(outcome) %>% 
      mutate(Dataset = "ITU")
  ) %>% 
  kbl(caption = "Observations per outcome") %>% 
  kable_custom()
```

And noted that the number of Gallup respondents decreases with age:

```{r}
gwp %>% 
  # filter(age %in% c("15 to 19", "50 to 54", "85 to 89")) %>% 
  group_by(age) %>% 
  summarise(
    n = quantile(n, probs = c(.1, .5, .9)),
    quantile = c("10%", "50%", "90%")
  ) %>% 
  pivot_wider(names_from = quantile, values_from = n) %>% 
  kbl(caption = "Quantiles of numbers of observations per age group") %>% 
  kable_custom()
```

## ITU summary table

Here is a table summarising the ITU internet predictor over time to region average percentage and number of coutries.

```{r itu-summary-table}
#| column: page-right
#| tbl-cap: "Mean internet user percentages across regions and time."
#| label: tbl-itusummary

itu %>%
  select(region, country, year, internet) %>%
  mutate(internet = internet * 100) %>%
  pivot_wider(names_from = year, values_from = internet) %>%
  select(-country) %>%
  tbl_summary(
    by = region,
    missing = "no",
    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
  ) %>%
  add_overall(col_label = "Total") %>%
  as_kable_extra(caption = "ITU summary") %>%
  row_spec(0, bold = TRUE) %>%
  kable_custom()
```

@@

:::{.panel-tabset .column-body-outset-right}

### Static

```{r trends-regions, message = FALSE}
#| fig-width: 10
#| fig-height: 8
#| fig-cap: "Trends in all variables across regions"
#| label: fig-trends-regions

@@

itu <- read_rds("data/itu.rds") %>%
  select(
    region, country, year,
    Internet = internet,
    Mobile = mobile,
  ) %>%
  # Truncate mobile percentages for figure
  mutate(Mobile = if_else(Mobile > 1.5, NaN, Mobile)) %>%
  pivot_longer(
    c(Internet, Mobile),
    names_to = "outcome", values_to = "val"
  )

@@

p1 <- tmp_country %>%
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value (%)",
    # Display percentages
    labels = ~. * 100,
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(
      group = interaction(country, outcome), 
      text = str_glue("{country} {year(year)} ({percent(mean)})")
    ),
    alpha = .45, size = .3, color = "dodgerblue1"
  ) +
  # geom_line(
  #   data = tmp_region %>% mutate(year = make_date(year)),
  #   aes(
  #     y = .fitted, 
  #     group = interaction(region, outcome),
  #     text = str_glue("{region} {year(year)} ({percent(.fitted)})")
  #   ),
  #   alpha = 1, size = .6, color = "dodgerblue4"
  # ) +
  # geom_line(
  #   data = tmp_world %>% mutate(year = make_date(year)),
  #   aes(
  #     y = .fitted, 
  #     group = interaction(region, outcome),
  #     text = str_glue("{region} {year(year)} ({percent(.fitted)})")
  #   ),
  #   alpha = 1, size = .8, color = "dodgerblue4"
  # ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    # aspect.ratio = 1,
    legend.position = "none",
    panel.spacing.x = unit(4, "pt"),
    panel.spacing.y = unit(6, "pt")
  )
p1
```

```{r include = FALSE}
agg_png(
  "figures/Trends-data.png",
  width = W, height = W*0.85, units = "in", res = 300
)
p1
dev.off()
```

### Interactive

```{r out.height = 860}
#| fig-cap: "Trends in all variables across regions. Hover over years to show the country's name."
#| label: fig-trends-regions-i
gp <- ggplotly(p1, tooltip = "text")
gp %>% 
  layout(
    margin = list(t = 30, r = 20, b = 40, l = 30),
    width = 840, height = 840
    )
```

### HDI

```{r fig.height = 1.8}
read_rds("data/itu.rds") %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, hdi)) +
  scale_y_continuous(
    "Value",
    labels = ~percent(., .1),
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(
      group = country, 
      text = str_glue("{country} {year(year)} ({hdi})")
    ),
    alpha = .45, size = .3, color = "dodgerblue1"
  ) +
  facet_wrap(
    ~ region,
    scales = "free_y",
    nrow = 1,
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    # aspect.ratio = 1,
    legend.position = "none",
    panel.spacing.x = unit(4, "pt"),
    panel.spacing.y = unit(6, "pt"),
    axis.title.y = element_blank()
  )
```

:::

### 2022-06-30 01-models.Rmd
Small fixes
Don't load anything in .Rprofile
wip 2022-06-30

```{r setup}
#| cache: false
# Packages
library(tidyverse)
library(knitr)
library(posterior)
library(ragg)
library(here)
library(scales)
library(bayestestR)
library(kableExtra)
library(memoise)
library(cachem)
library(ggh4x)
library(cmdstanr)
library(brms)
library(multidplyr)

cluster <- new_cluster(3)

cd <- cache_disk("memoise_cache", max_size = Inf)
```

Here we discuss the models. The models are fitted in `models.R`. We submit that to our local SLURM cluster with `submit.sh`.

@@

Model 1 is a three-level bayesian multivariate meta-regression model that simultaneously estimates trends over time for the outcome (e.g. Life satisfaction) and internet adoption, with shared covariance matrices over the two outcomes across regions and countries. It also includes sex and the sex by time interaction predictors for the outcomes. The parameters are also treated as random across the age groups, and the age by country, and age by region interactions. We fit the model separately for each outcome. In this model, internet adoption is treated as Beta-distributed and the outcomes are treated as gaussian.

The GBD data are estimates with standard errors, and thus suggest that a model that incorporates the SEs would be appropriate. For this reason, and for reducing computational complexity, we have reshaped the GWP data similarly to aggregates per cell (mean and SE for each country \* year \* sex \* age). The one downside of this modelling strategy is that it does not converge for self-harm. Therefore we estimate the model with SEs for all outcomes except self-harm, where we set the SEs to zero. In addition, for self-harm, we remove the $age:country$ random effects.

We write the model as

$$
\begin{align}
y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2}v_i) \\

\mu^y_i &= \alpha^{y}_{0} + \beta^{y}_{0\text{region}[i]} + \gamma^{y}_{0\text{country}[i]} + \delta^{y}_{0\text{age}[i]} + \zeta^{y}_{0\text{age:region}[i]} + \eta^{y}_{0\text{age:country}[i]} \\ &(\alpha^{y}_{1} + \beta^{y}_{1\text{region}[i]} + \gamma^{y}_{1\text{country}[i]} + \delta^{y}_{1\text{age}[i]} + \zeta^{y}_{1\text{age:region}[i]} + \eta^{y}_{1\text{age:country}[i]})\text{Time}_i + \\
&(\alpha^{y}_{2} + \beta^{y}_{2\text{region}[i]} + \gamma^{y}_{2\text{country}[i]} + \delta^{y}_{2\text{age}[i]} + \zeta^{y}_{2\text{age:region}[i]} + \eta^{y}_{2\text{age:country}[i]})\text{Sex}_i + \\
&(\alpha^{y}_{3} + \beta^{y}_{3\text{region}[i]} + \gamma^{y}_{3\text{country}[i]} + \delta^{y}_{3\text{age}[i]} + \zeta^{y}_{3\text{age:region}[i]} + \eta^{y}_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\ \\

x_i &\sim \text{Beta}(\mu^x_i, \phi) \\ 
\text{logit}(\mu^x_i) &= \alpha^{x}_{0} + \beta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + (\alpha^x_{1} + \beta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
\end{align}
$$

$$
\begin{align}

\left[\begin{array}{c}
\beta^y_{0\text{region}} \\ \beta^y_{1\text{region}}\\ 
\beta^y_{2\text{region}} \\ \beta^y_{3\text{region}} \\
\beta^x_{0\text{region}} \\ \beta^x_{1\text{region}}
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{region}),

\left[\begin{array}{c}
\gamma^y_{0\text{country}} \\ \gamma^y_{1\text{country}} \\ 
\gamma^y_{2\text{country}} \\ \gamma^y_{3\text{country}} \\
\gamma^x_{2\text{country}} \\ \gamma^x_{3\text{country}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{country}),

\left[\begin{array}{c}
\delta^y_{0\text{age}} \\ \delta^y_{1\text{age}} \\ 
\delta^y_{2\text{age}} \\ \delta^y_{3\text{age}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{age}), \\

\left[\begin{array}{c}
\zeta^y_{0\text{age:region}} \\ \zeta^y_{1\text{age:region}} \\ 
\zeta^y_{2\text{age:region}} \\ \zeta^y_{3\text{age:region}}
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{age:region}),

\left[\begin{array}{c}
\eta^y_{0\text{age:country}} \\ \eta^y_{1\text{age:country}} \\ 
\eta^y_{2\text{age:country}} \\ \eta^y_{3\text{age:country}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{age:country})

\end{align}
$$ {#eq-model1}

Where $y_i$ are the outcomes, $x_i$ the internet adoption values, and $v_i$ indicate the known sampling variances. We also fit this same model but using the mobile broadband subscriptions as $x$ ("Model 4").

@@

$$
\begin{align*}
y_i &\sim \text{Normal}(\mu_i, \sigma^{2}v_i) \\

\mu_i &= \alpha_{0} + \beta_{0\text{region}[i]} + \gamma_{0\text{country}[i]} + \delta_{0\text{age}[i]} + \zeta_{0\text{age:region}[i]} + \eta_{0\text{age:country}[i]} \\ &(\alpha_{1} + \beta_{1\text{region}[i]} + \gamma_{1\text{country}[i]} + \delta_{1\text{age}[i]} + \zeta_{1\text{age:region}[i]} + \eta_{1\text{age:country}[i]})\text{Time}_i + \\
&(\alpha_{2} + \beta_{2\text{region}[i]} + \gamma_{2\text{country}[i]} + \delta_{2\text{age}[i]} + \zeta_{2\text{age:region}[i]} + \eta_{2\text{age:country}[i]})\text{Sex}_i + \\
&(\alpha_{3} + \beta_{3\text{region}[i]} + \gamma_{3\text{country}[i]} + \delta_{3\text{age}[i]} + \zeta_{3\text{age:region}[i]} + \eta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
&(\alpha_{4} + \beta_{4\text{region}[i]} + \gamma_{4\text{country}[i]} + \delta_{4\text{age}[i]} + \zeta_{4\text{age:region}[i]} + \eta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i + \\
&(\alpha_{5} + \beta_{5\text{region}[i]} + \gamma_{5\text{country}[i]} + \delta_{5\text{age}[i]} + \zeta_{5\text{age:region}[i]} + \eta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i \\ \\

\left[\begin{array}{c}
\beta_{0\text{region}} \\ \beta_{1\text{region}} \\ 
\beta_{2\text{region}} \\ \beta_{3\text{region}} \\
\beta_{4\text{region}} \\ \beta_{5\text{region}} 
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{region}),

\left[\begin{array}{c}
\gamma_{0\text{country}} \\ \gamma_{1\text{country}} \\ 
\gamma_{2\text{country}} \\ \gamma_{3\text{country}} \\
\gamma_{2\text{country}} \\ \gamma_{3\text{country}} 
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{country}),

\left[\begin{array}{c}
\delta_{0\text{age}} \\ \delta_{1\text{age}} \\ 
\delta_{2\text{age}} \\ \delta_{3\text{age}} \\
\delta_{4\text{age}} \\ \delta_{5\text{age}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{age}), \\

\left[\begin{array}{c}
\zeta_{0\text{age:region}} \\ \zeta_{1\text{age:region}} \\ 
\zeta_{2\text{age:region}} \\ \zeta_{3\text{age:region}} \\
\zeta_{4\text{age:region}} \\ \zeta_{5\text{age:region}}
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{age:region}),

\left[\begin{array}{c}
\eta_{0\text{age:country}} \\ \eta_{1\text{age:country}} \\ 
\eta_{2\text{age:country}} \\ \eta_{3\text{age:country}} \\
\eta_{4\text{age:country}} \\ \eta_{5\text{age:country}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{age:country})
\end{align*}
$$ {#eq-model1}

Where $\text{Internet}^{\text{t-1}}_i$ is the within-country centered 1-year-lagged internet user proportion. We then also fit this model but using the mobile broadband subscription numbers instead of the internet user proportions ("Model 3").

@@

Next, we display the population-level parameters of each model, along with their numberical HMC diagnostics (ESS and Rhat values).

```{r}
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = fct_inorder(outcome))
```

@@

Rhats should approach 1, and the latter should approach the number of hmc iterations (about 4000). We first calculate these posterior summaries for each population level parameter for each outcome and model.

```{r model-diagnostics}
parameter_summary <- function(outcome, model) {
  path <- str_glue("models/brm-{outcome}-{model}.rds")
  as_draws_df(
    readRDS(path), 
    variable = c("^b_", "^sd_", "^cor_"), 
    regex = TRUE
  ) %>%
    summarise_draws(
      mean, sd,
      ~quantile2(., probs = c(.025, .5, .975)),
      pd = ~pd(as.numeric(.)), 
      samples = length, 
      default_convergence_measures()
    )
}
parameter_summary <- memoise(parameter_summary, cache = cd)

fits_parameters <- tibble(
  path = list.files("models/", full.names = TRUE)
) %>% 
  separate(path, c("brm", "outcome", "model"), sep = "-") %>% 
  select(-brm) %>% 
  mutate(model = str_extract(model, "[0-9]")) %>% 
  mutate(parameters = map2(outcome, model, ~parameter_summary(.x, .y))) %>% 
  unnest(parameters)
```

@@

### Rhats

Take a look at distributions with worst rhats

```{r}
#| eval: false
x <- readRDS("models/brm-Depression-3.rds")
rhat(x, pars = variables(x)[1:10])
bads <- fits_parameters %>% 
  group_by(outcome, model) %>% 
  arrange(outcome, model, desc(rhat)) %>% 
  slice(1:4)
bads

foo <- function(outcome, model) {
  bads <- filter(bads, outcome == {{outcome}}, model == {{model}})
  x <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  agg_png(
    str_glue("diagnostics/bads-{outcome}-{model}.png"),
    width = W, height = W, units = "in", res = 200
  )
  pairs(x$fit, pars = pull(bads, variable))
  title(sub = str_glue("bads-{outcome}-{model}"))
  dev.off()
}
foo <- memoise(foo, cache = cd)
fits %>% 
  crossing(model = 1:4) %>% 
  mutate(walk2(outcome, model, foo))
```

@@

Browse these figures at `diagnostics/`

```{r}
#| eval: false
pairsplot <- function(path) {
  x <- readRDS(str_glue(here(path)))
  agg_png(
    str_glue("diagnostics/{path}.png"),
    width = W*1.5, height = W*1.5, units = "in", res = 200
  )
  pairs(x$fit, pars = variables(x)[1:22])
  title(sub = path)
  dev.off()
}
pairsplot <- memoise(pairsplot, cache = cd)
list.files("models", full.names = TRUE) %>% 
  walk(pairsplot)
```

@@

```{r ppcheck-density}
#| eval: false
#| column: page-right
#| fig-height: 6
#| fig-width: 9
#| fig-cap: "Graphical posterior predictive check by region (Model 1). Thin red lines indicate model replicates, whereas the blue lines indicate data; the model is mostly in smooth agreement with data, but has greater discrepancies in some regions (e.g. Anglo Depression)."
#| label: fig-ppcheck-1

pp_check_fun <- function(outcome, model) {
  path <- str_glue("models/brm-{outcome}-{model}.rds")
  fit <- readRDS(path)
  pp_check(
    fit,
    ndraws = 10,
    type = "dens_overlay_grouped",
    group = "region",
    resp = "val",
    newdata = fit$data
  )[[1]]
}
pp_check_fun <- memoise(pp_check_fun, cache = cd)

cluster_copy(cluster, "pp_check_fun")
cluster_library(cluster, c("tidyverse", "bayesplot", "brms"))
pp_checks <- tibble(
  path = list.files("models/", full.names = TRUE)
) %>% 
  separate(path, c("brm", "outcome", "model"), sep = "-") %>% 
  select(-brm) %>% 
  mutate(model = str_extract(model, "[0-9]")) %>% 
  mutate(pp_check = map2(outcome, model, ~pp_check_fun(.x, .y))) %>% 
  unnest(pp_check)

pp_checks %>%
  filter(model == 1) %>% 
  ggplot(aes(value, col = is_y, alpha = is_y, group = rep_id)) +
  scale_color_brewer(palette = "Set1") +
  scale_alpha_manual(values = c(.2, 1)) +
  stat_density(
    geom = "line",
    size = .75,
    position = position_identity()
  ) +
  labs(x = "Value", y = "Density") +
  facet_grid2(
    outcome ~ group,
    scales = "free", independent = "x",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    legend.position = "none",
    panel.spacing = unit(3, "pt"),
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  )
```

>>>>

```{r setup, include = FALSE}
#| cache: false
# Packages
library(tidyverse)
library(knitr)
library(posterior)
library(ragg)
library(here)
library(scales)
library(bayestestR)
library(kableExtra)
library(memoise)
library(cachem)
library(ggh4x)
library(cmdstanr)
library(brms)

# Common options
source("_common.R")
cd <- cache_disk("memoise_cache", max_size = Inf)
```

Here we discuss the models. The code for estimating these models is in `models.R`. We submit that to our local HPC with SLURM scheduler with `submit.sh`.

@@

Model 1 is a two-level probabilistic multivariate meta-regression model that simultaneously predicts the health (e.g. Life satisfaction) and internet variables (e.g. internet adoption) from time, sex, and time by sex interactions. These regression coefficients are modelled as multivariate normal distributed over countries, age groups, and the country by age groups. The latter clustering was dropped from the mental health variables because of nonconvergence due to lack of variance in data ($\Sigma^\text{age:country} = 0$). The country-level covariance matrices are shared across the two outcomes so we can assess correlations between countries' intercepts and slopes over the two outcomes.

Because we are modelling meta-analytic estimates (GBD) and aggregated scores (GWP), we also incorporate the aggregates' standard errors in the model to weight the observations on their corresponding uncertainties. Due to nonconvergence, we set the SEs to zero for self-harm ($v = 0$).

$$
\begin{align}
y_i &\sim \text{Normal}(\mu^y_i, \sigma^{y2}v_i) \\
x_i &\sim \text{Normal}(\mu^x_i, \sigma^{x2}) \\ 
\mu^y_i &= \alpha^{y}_{0} + \beta^{y}_{0\text{country}[i]} + \gamma^{y}_{0\text{age}[i]} + \delta^{y}_{0\text{age:country}[i]} + \\ 
&(\alpha^{y}_{1} + \beta^{y}_{1\text{country}[i]} + \gamma^{y}_{1\text{age}[i]} + \delta^{y}_{1\text{age:country}[i]})\text{Time}_i + \\
&(\alpha^{y}_{2} + \beta^{y}_{2\text{country}[i]} + \gamma^{y}_{2\text{age}[i]} + \delta^{y}_{2\text{age:country}[i]})\text{Sex}_i + \\
&(\alpha^{y}_{3} + \beta^{y}_{3\text{country}[i]} + \gamma^{y}_{3\text{age}[i]} + \delta^{y}_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\
\mu^x_i &= \alpha^{x}_{0} + \beta^{x}_{0\text{country}[i]} + (\alpha^x_{1} + \beta^{x}_{1\text{country}[i]})\text{Time}_i \\
\pmb{\beta} &\sim MVN(\pmb{0}, \Sigma^\text{country}) \\
\pmb{\gamma} &\sim MVN(\pmb{0}, \Sigma^\text{age}) \\
\pmb{\delta} &\sim MVN(\pmb{0}, \Sigma^\text{age:country})
\end{align}
$$ {#eq-model1}

@@

$$
\begin{align}
y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i) \\
\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\ 
&(\alpha_{1} + \beta_{1\text{country}[i]} + \gamma_{1\text{age}[i]} + \delta_{1\text{age:country}[i]})\text{Time}_i + \\
&(\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
&(\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\
&(\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i \\
&(\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i \\
\pmb{\beta} &\sim MVN(\pmb{0}, \Sigma^\text{country}) \\
\pmb{\gamma} &\sim MVN(\pmb{0}, \Sigma^\text{age}) \\
\pmb{\delta} &\sim MVN(\pmb{0}, \Sigma^\text{age:country})
\end{align}
$$ {#eq-model2}

Where $\text{Internet}^{\text{t-1}}_i$ is the within-country centered 1-year-lagged internet user proportion (or mobile subscriptions).

@@

Next, we display the population-level parameters of each model, along with their numerical HMC diagnostics (ESS and Rhat values).

```{r}
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = fct_inorder(outcome))

# The files are huge and unwieldy to work with. We create smaller files for each by dropping samples of the age:country interaction random effects. It is then easier to post-process the models.
dir.create("models-small", FALSE)

replace_chain <- function(x) {
  x %>%
    select(
      -starts_with("r_1"),
      -starts_with("r_2"),
      -starts_with("r_3"),
      -starts_with("z_1"),
      -starts_with("z_2"),
      -starts_with("z_3"),
      -starts_with("r_age:country"),
      -starts_with("L_")
    )
}

replace_chain_all <- function(x) {
  if (!file.exists(str_glue("models-small/{x}"))) {
    message(x)
    out <- readRDS(str_glue("models/{x}"))
    out$fit@sim$samples <- map(1:4, ~replace_chain(out$fit@sim$samples[[.]]))
    saveRDS(out, str_glue("models-small/{x}"), compress = FALSE)
  }
}

walk(
  list.files("models"),
  ~replace_chain_all(.x)
)
```

@@

Rhats should approach 1, and the latter should approach the number of hmc iterations. We first calculate these posterior summaries for each population level parameter for each outcome and model.

```{r model-diagnostics}
parameter_summary <- function(outcome, model) {
  path <- str_glue("models-small/brm-{outcome}-{model}.rds")
  as_draws_df(
    readRDS(path), 
    variable = c("^b_", "^sd_", "^cor_"), 
    regex = TRUE
  ) %>%
    summarise_draws(
      mean, sd,
      ~quantile2(., probs = c(.025, .5, .975)),
      pd = ~pd(as.numeric(.)), 
      samples = length, 
      default_convergence_measures()
    )
}
parameter_summary <- memoise(parameter_summary, cache = cd)

fits_parameters <- tibble(
  path = list.files("models-small/", pattern = ".rds$", full.names = FALSE)
) %>% 
  separate(path, c("brm", "outcome", "model"), sep = "-") %>% 
  select(-brm) %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  arrange(outcome) %>% 
  mutate(model = str_extract(model, "[0-9]")) %>% 
  mutate(parameters = map2(outcome, model, ~parameter_summary(.x, .y))) %>% 
  unnest(parameters)
```

@@

@@

Have the chains converged? Are there divergences?

For each model, we draw a scatterplot matrix of parameters with worst rhats. Browse these figures at `diagnostics/`

```{r}
# Function to draw a pairsplot of variables `v` of model in `path` 
pairsplot <- function(path, v) {
  if (!file.exists(str_glue("diagnostics/{basename(path)}.png"))) {
    x <- readRDS(here(path))
    agg_png(
      str_glue("diagnostics/{basename(path)}.png"),
      width = W*1.2, height = W*1.2, units = "in", res = 160
    )
    pairs(x$fit, pars = v)
    title(sub = path)
    dev.off()
  }
}

# Draw pairsplot for 10 worst rhats per model
fits_parameters %>% 
  group_by(outcome, model) %>% 
  arrange(outcome, model, desc(rhat)) %>% 
  slice(1:10) %>% 
  ungroup() %>% 
  group_by(outcome, model) %>% 
  summarise(v = list(variable)) %>% 
  mutate(path = str_glue("models-small/brm-{outcome}-{model}.rds")) %>% 
  ungroup() %>% 
  {walk2(.$path, .$v, ~pairsplot(.x, .y))}
```

@@

Do the models reproduce the observed data?

```{r ppcheck-density}
#| fig-height: 6
#| fig-width: 9
#| fig-cap: "Graphical posterior predictive check by region. Thin red lines indicate model replicates, whereas the blue lines indicate data."
#| label: fig-ppcheck-1

pp_check_fun <- function(outcome, model) {
  path <- str_glue("models/brm-{outcome}-{model}.rds")
  fit <- readRDS(path)
  pp_check(
    fit,
    ndraws = 10,
    type = "dens_overlay",
    resp = "val",
    newdata = fit$data
  )[[1]]
}
pp_check_fun <- memoise(pp_check_fun, cache = cd)

pp_checks <- tibble(
  path = list.files("models/", full.names = TRUE)
) %>% 
  separate(path, c("brm", "outcome", "model"), sep = "-") %>% 
  select(-brm) %>% 
  mutate(model = str_extract(model, "[0-9]")) %>% 
  mutate(pp_check = map2(outcome, model, ~pp_check_fun(.x, .y))) %>% 
  unnest(pp_check)

pp_checks %>%
  slice_sample(prop = .1) %>% 
  ggplot(aes(value, col = is_y, alpha = is_y, group = rep_id)) +
  scale_color_brewer(palette = "Set1") +
  scale_alpha_manual(values = c(.2, 1)) +
  stat_density(
    geom = "line",
    size = .75,
    position = position_identity()
  ) +
  labs(x = "Value", y = "Density") +
  facet_grid2(
    model~outcome,
    scales = "free", independent = "y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    legend.position = "none",
    panel.spacing = unit(3, "pt"),
    axis.title = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  )
```
